---
title: "Probe into relationship between Covid-19 and Crime in LA"
author: "Tao Huang"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
---




<br>

```{r setup, message=FALSE, echo=FALSE, warning=FALSE}

library(data.table)
library(tidyverse)
library(dplyr)
library(plotly)
library(DT)
library(knitr)

library(rvest) 
library(httr) 
library(stringr)
library(jsonlite)
library(ggplot2)
library(lubridate)
library(patchwork)


# Initialize code chunk options
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  eval=TRUE,
  echo = FALSE,
  cache = FALSE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618,
  out.width = "700px",
  class.source = "code-r")
```

```{css, echo = FALSE}
.code-r { /* Code block */
  font-size: 15px;
}

.code-r-small { /* Code block */
  font-size: 10px;
}
```

<br>

# Project Introduction

In 2020, the covid-19 epidemic has swept the world, and the United States is no exception. The impact of this epidemic is all-round, whether economy, politics, diplomacy, environment, or even urban security have all been affected a lot. Los Angeles is the second largest city in the United States and the largest city in California. It is known for its ethnic diversity and economic development. Therefore, I think Los Angeles is a representative American city, and decided to choose Los Angeles as a key research object to explore the urban security situation under the covid-19.

<br>

----

# Data & API
<br>
LA_raw_crime：The API comes from Los Angeles city data. The data collection includes all data from January 2017 to October 7, 2020. (https://data.lacity.org/resource/2nrs-mtv8.json)


<br>


LA_raw_covid：Including all the data from March 10, 2020 to October 7, 2020 in Los Angeles County. In order to facilitate the comparison of the impact of the emergence of covid-19 on the psychological and economic aspects of residents, which may lead to an increase in the crime rate, I Set the numbers of covid-19 data before March to 0. The data comes from County of Los Angeles Public Health. (https://raw.githubusercontent.com/Icygrey/pm566_lab12_hw5/main/latimes-place-totals.csv)

<br>

----


# Method and Process
<br>

The Method and Process is as follows:

1.Create a time series axis of crime frequency from 2017 to 2020 and compare them: 
<br>
Extract the data of 2017, 2018, 2019 and 2020 from Lacity.og, clean and organize the data, then use data.table to calculate the cumulative crime frequency, and finally use plotly to make a time series graph.
<br>
<br>
2.Create interactive hotmaps to find areas with high incidence of covid-19 and crime, and try to find connections: 
<br>
Clean the data, extract all the latitude and longitude in the data set, then approximate the latitude and longitude, calculate the frequency, and finally use leaflet to make a map.
<br>

<br>
3.Text mining to view the most frequent types of crimes in 2019 and 2020: 
<br>
Use regular expressions to extract the keywords in the crime description, then extract the most frequent words, and use ggplot to make a bar graph.



<br>


----


# Results
<br>

## 1.Create a time series


```{r, class.source="code-r-small"}

source("process_COVID_data.R")
# data pre-processing
##covid
#calculate the numbers of cumulative positive persons in the ending day of each day in 2020.





#####get "la_crime"
la_raw_crime<-data.table(la_raw_crime)#change data.frame to model of data.table  /or directly use fread("csv..")
#cumulative_criminal_persons

#get  "la_crime_freq"
la_crime_freq<-la_raw_crime[,ymd:=ymd(as.Date(la_raw_crime$date_rptd))]
la_crime_freq<-data.table(data.frame(table(la_crime_freq$ymd),stringsAsFactors=F))
la_crime_freq<-la_crime_freq[,cumulative_criminal_persons:=cumsum(la_crime_freq$Freq)]
la_crime_freq<-la_crime_freq[,ymd:=ymd(la_crime_freq$Var1)]
la_crime_freq<-la_crime_freq[0:279]





crime17181920<-la_crime_freq[,cum2019:=crime2019$cum2019]
crime17181920<-la_crime_freq[,cum2018:=crime2018$cum2018]
crime17181920<-la_crime_freq[,cum2017:=crime2017$cum2017]



fig <- plot_ly(crime17181920, x = ~ymd, y = ~cumulative_criminal_persons, name = 'cum2020', type = 'scatter', mode = 'lines') 
fig <- fig %>% add_trace(y = ~cum2019, name = 'cum2019', mode = 'lines') 
fig <- fig %>% add_trace(y = ~cum2018, name = 'cum2018', mode = 'lines') 
fig <- fig %>% add_trace(y = ~cum2017, name = 'cum2017', mode = 'lines') 
```
The plot shows blow.
```{r}
fig
```

By comparing the frequency of cumulative crime in LA for 4 years (2017-2020), it can be clearly found that the frequency of cumulative crime in LA in 2020 (blue line) has decreased significantly, especially after the covid-19 outbreak. (From February to March, the blue line starts to deviate from the other lines.)

<br>





## 2.Create interactive Heat Maps

```{r, class.source="code-r-small"}
##the frequency of crime：

la_crime<-la_raw_crime[,ymd:=ymd(as.Date(la_raw_crime$date_rptd))]

#round procss of lat and lon
la_crime<-la_raw_crime[,nlat:=round(as.numeric(lat),2)]
la_crime[,nlon:=round(as.numeric(la_crime$lon),2)]

##the frequency of crime in 2020
ll_freq<-la_crime[,ll:=paste(nlon,nlat,sep = ",")] 
ll_freq<-data.table(data.frame(table(ll_freq$ll),stringsAsFactors=F))


##extract lon & lat from text.
nlon2<-data.frame(as.numeric(str_extract(ll_freq$Var1,
                   "-[[:digit:]]+.[[:digit:]]+"
                   )))

nlat2<-data.frame(as.numeric(str_extract(ll_freq$Var1,
                   "(?<=,)[[:digit:]]+.[[:digit:]]+|(?<=,)[[:digit:]]+"
                   )))

ll_freq[,nlon:=nlon2]
ll_freq[,nlat:=nlat2]

## Los Angeles Crime distributed MAP in 2020
library(leaflet)
pal <- colorNumeric(palette = c("white","red","black"),domain = ll_freq$Freq)

crime_map<-leaflet(ll_freq) %>%
  addProviderTiles(providers$Stamen.Toner)%>%
  addCircles(lng=~nlon,lat=~nlat,fillColor = ~pal,fillOpacity = 0.6,color = ~pal(Freq),
             label = paste("Crime frequency:",ll_freq$Freq,sep = ""),labelOptions =(noHide = F))%>%
  addLegend("bottomright", pal = pal, values = ~Freq,
    title = "Crime Cases",
    opacity = 1
  )

##############################################



la_covid<-covid[county %in% c("Los Angeles")]
la_covid<-la_covid[date=="2020-10-11"]
la_covid<-la_covid[,cases:=as.numeric(la_covid$confirmed_cases)]


library(leaflet)
##popups
content <- paste(sep = "<br/>",
  "<b><a href='http://www.samurainoodle.com'>Samurai Noodle</a></b>",
  "606 5th Ave. S",
  "Seattle, WA 98138"
)


pal <- colorNumeric(palette = c("white","red","black"),domain = la_covid$cases)


covid_map<-leaflet(la_covid) %>%
  addProviderTiles(providers$Stamen.Toner)%>%
  addCircleMarkers(lng=~x,lat=~y,color = ~pal(cases),
                    stroke = FALSE,radius=8, fillOpacity = 0.5,
                   label=paste(la_covid$place,"(cases):",la_covid$confirmed_cases, sep = ""),
                   labelOptions =(noHide = F))%>%
  addLegend("bottomright", pal = pal, values = ~cases, 
            title = "Covid-19 Cases",
            opacity = 1)

```



### Crime Heat Map in LA

```{r}
crime_map
```


### Covid-19 confirmed population Heat Map in LA

```{r}
covid_map
```

## {-}

<br>

Through the comparison of the two Heat Maps, we can find that downtown and central-southern Los Angeles are more likely to become covid-19 outbreak points and have a higher frequency of crime in 2020.(See the dark red and black areas in the map)
<br>


<br>

## 3.Text mining
<br>
```{r plot1, class.source="code-r-small"}
#2019
text_2019<-data.frame(str_extract(text_2019$desc,
                             "[[:alpha:]]+"
                             ))
data2019<-data.table(table(text_2019) %>% sort(decreasing = TRUE))


##text mining 2020
text_2020<-data.frame(str_extract(la_crime$crm_cd_desc,
                             "[[:alpha:]]+"
                             ))
data2020<-data.table(table(text_2020) %>% sort(decreasing = TRUE))

table2019<-data2019 %>%
  top_n(20,N) %>%     #top_n(x,n,wt)  ...x has been piped before (x = token)
  ggplot(aes(fct_reorder(text_2019,N) ,N)) + geom_col() + coord_flip() 

table2020<-data2020 %>%
  top_n(20,N) %>%     #top_n(x,n,wt)  ...x has been piped before (x = token)
  ggplot(aes(fct_reorder(text_2020,N) ,N)) + geom_col() + coord_flip() 



```





## {.tabset}

### Types of crime ranking in 2020

```{r p1}
table2020
```

### Types of crime ranking in 2019

```{r p2}
table2019
```

## {-}
From the figures above, It can be found that the frequency of economic crimes (Theft, Burglary) in 2019 and 2020 both occupy the first and second places.

<br>



<br>

## 4. Create overlapped barplot
<br>

```{R, class.source="code-r-small"}

data2020$percent<-round(data2020$N/sum(data2020$N),3) 
data2019$percent<-round(data2019$N/sum(data2019$N),3)


test<-merge(data2020,data2019,by.x="text_2020",by.y ="text_2019") %>% arrange(desc(N.x))


fig_percent <- plot_ly(test, alpha=0.5,x = ~text_2020,y = ~percent.x, name = '2020 Crime percent',type = 'bar')
fig_percent <- fig_percent %>% add_trace(y = ~percent.y, name = '2019 Crime percent',type = 'bar')  %>% layout(barmode = "overlay")

```

### Compare the frequency of various crimes in 2019 and 2020

```{r}
fig_percent
```

<br>

In 2020, Los Angeles economic crimes (Theft, Burglary) accounted for a decrease in the proportion of total crimes in the year compared with 2019. I guess that this may be due to the federal government's relief payments, large-scale shops closed, and people reduced their outings, thus avoiding theft and robbery.
<br>
In addition, we can clearly see the decrease in the frequency and proportion of battery crime, and the frequency of occurrence has dropped from the third place in 2019 to the fifth place. On the contrary, the frequency of vehicle occurrence has risen to third place. This is consistent with our impression that during the epidemic, people prefer to use private cars to travel, which may indirectly increase the number of traffic accidents.

<br>

----


# Conclusion
<br>


The crime frequency in Los Angeles in 2020 has been significantly reduced since February compared to previous years. I guess, this may be because the outbreak of covid-19 has allowed more residents to choose not to go out, thus reducing the risk of harm. In addition, through the comparison of heat maps, communities with densely populated (downtown) and low-income groups (central-southern Los Angeles) are more likely to become covid-19 outbreak points and have a higher frequency of crime. 

Besides, through text mining, we found that crimes in the past two years were concentrated in economic cases (Theft and Burglary), and In 2020, Los Angeles economic crimes accounted for a decrease in the proportion of total crimes in the year compared with 2019. I guess that this may be due to the large-scale shops closed, and people reduced their outings, thus avoiding theft and robbery. And Federal government relief payments may also have played an important role.




<br>
<br>